### 2018-01-11 project.tex
Prop 2.3 attempt
Proposition 2 part 1

  \begin{definition}
    A topology is...
  \end{definition}

  \begin{theorem}
    An arbitrary intersetion of closed sets is closed.
  \end{theorem}

  \begin{proof}
    Because.
  \end{proof}

\end{document}

>>>>

  \begin{proposition}
      Any finite union of closed sets is closed, and any arbitrary intersection of closed sets is closed.
  \end{proposition}

  \begin{proof}
  	Proposition 1
  	\newline
	X $\in$ $\tau$
	\newline
	If U $\subseteq$ X $\wedge$ X$\setminus$U $\in \tau$ then X$\setminus\bigcap$U $\in \tau$
	\newline
	If U, V $\subseteq$ X $\wedge$ X$\setminus$U $\in \tau$  $\wedge$ X$\setminus$V $\in \tau$ then X$\setminus$U $\cup$ V $\in \tau$
  \end{proof}

	\begin{proposition}
		A set K in a topological space X is closed if and only if K contains all its limit points.
	\end{proposition}
	\begin{proof}
		Proposition 2 Part 1 - Prove if K contains all its limit points then that implies X$\setminus$K $\in \tau$
		\newline
		$\exists$ x, z, $\alpha, \beta, \lambda, \epsilon \in$ X
		\newline
		K $\subseteq$ X, B $\subseteq$ X, C $\subseteq$ X
		\newline
		x, z $\in$ K, K = $\lbrace$ y $\mid$ x $\leq$ y $\leq$ z $\rbrace$
		\newline
		x, $\alpha, \beta \in$ B, B = $\lbrace \left( \alpha, \beta \right) \mid \alpha <$ x $< \beta  \rbrace$
		\newline
		z, $\lambda, \epsilon \in$ C, C = $\lbrace \left( \lambda, \epsilon \right) \mid \lambda <$ z $< \epsilon \rbrace$
		\newline
		K $\cap$ B = $[$ x, $\beta  )$, x $\neq \beta \therefore$ x is a limit point.
		\newline
		K $\cap$ C = $( \lambda$, z $]$, z $\neq \lambda \therefore$ z is a limit point.
		\newline
		x, z $\in$ K, K = $\lbrace$ y $\mid$ x $\leq$ y $\leq$ z $\rbrace \therefore$ K is closed $\Rightarrow$ X$\setminus$K $\in \tau$
		\newline
	\end{proof}
	\begin{proof}
	Proposition 2 Part 2 - Prove if X$\setminus$K $\in \tau$ then that implies that K contains all of its limit points.
	\end{proof}
\end{document}
